Survivable Set Connectivity

### 2015-05-13 draft.tex
changes to end of section 1

The paper is organized as follows. Sections 2, 3, and 4 provide the background necessary to understand the algorithm by Chalermsook et al. In Section 2, we present a natural integer linear programming formulation of the problem. Then, in Section 3, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm. In Section 4, we give a rounding scheme by Garg et al. known as RoundGKR, which the algorithm uses as a black box \cite{GKR}. We then pull together these concepts in Section 5 to present and analyze the approximation algorithm for SSC by Chalermsook et al. Finally, in Section 6, we present our own modification to the algorithm which improves the approximation ratio under special circumstances. We also conclude with ideas for potential further improvements.

>>>>

The paper is organized as follows. Sections 2, 3, and 4 provide the background necessary to understand the algorithm by Chalermsook et al. In Section 2, we present a natural integer linear programming formulation of the problem. Then, in Section 3, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm. In Section 4, we give a rounding scheme by Garg et al. known as RoundGKR, which the algorithm uses as a black box \cite{GKR}. We then pull together these concepts in Section 5 to present the approximation algorithm for SSC by Chalermsook et al. In Section 6, we analyze the performance of the algorithm. In Section 7, we present our own ideas for how the algorithm might be modified to improve its approximation ratio under special circumstances.
